Estimation of the road traffic sound levels in urban areas based on non-negative matrix factorization techniques

### 2018-08-31 revision/responseToreviewers.tex

\end{enumerate}

\section{Answers to Reviewer 2}

\begin{enumerate}
\item \emph{As the previous work has been already published, the authors should provide references to it and clearly state the new contributions of the presented paper. I believe there may be a substantial overlap with the authors' paper Gloaguena, J. R., Cana, A., Lagrangeb, M., $\&$ Petiotb, J. F. Estimation du niveau sonore du trafic routier au sein de mixtures sonores urbaines par la Factorisation en Matrices Non négatives, 2018.}

$\rightarrow$ The paper 'Gloaguen, J. R., Can, A., Lagrange, M., $\&$ Petiot, J. F. Estimation du niveau sonore du trafic routier au sein de mixtures sonores urbaines par la Factorisation en Matrices Non négatives, 2018' is a congress article without review submitted after the submission of the present paper. It deals with a similar approach but on a different sound corpus.  Furthermore, as it is written in french we chose to alternatively cite 'Gloaguen, J.R., Can, A., Lagrange, M., Petiot, J.F.: Estimating traffic noise levels using acoustic monitoring: A preliminary study' which is written in English and deals with the same corpus.

@@

\item \emph{Some sentences in the abstract are not well formulated and are hard to follow. E.g. "The task being to the best of our knowledge never been considered in the literature, we propose an experimental protocol to validate the studied approaches that complies with standard reproducible research recommendations." should be splitted, "being" should be omitted; "raise this kind of innovative approaches" - the verb "raise" is confusing; "based on non-negative factorization framework" - the word "matrix" is missing. The authors may want to be more specific about the obtained results.}

$\rightarrow$ The bastract have been rewritten to take those requests into account: 'The task is to the best of our knowledge never been considered in the literature. We propose\dots' (l 19-20), 'Among the technical issues that bring this kind of innovative approaches,\dots ' (l 12-13), 'several techniques based on non-negative matrix  factorization framework' (l 17-18).

@@

\item \emph{"Their spectra can be obtained and be a basis of W." The procedure is not clear and is only described in the experimental part. This sentence seems to mean that the matrix W is comprised of exemplars (e.g. see $http://www.cs.tut.fi/sgn/arg/music/tuomasv/chime-enhancement/pP4_gemmeke.pdf$), which is not the case. In supervised NMF framework, the basis matrix W is usually pre-trained applying NMF to the training data. It would be interesting to compare such approach to the proposed K-means procedure.}

$\rightarrow$ The K-means and NMF procedures can be considered as similar approaches for a clustering tool (see Ding et al., 2005), so it has not been tested.
A block diagram has been added to better explain the dictionary learning process shown in Figure 7 of the updated manuscript.

@@

\item \emph{One type of vehicles (passenger car) is addressed in the simulations. Authors may want to comment on why other types like motorcycles, which generate a palpable amount of noise and may have different acoustic characteristics, are not considered.}

$\rightarrow$ This important limitation of the presented study is now clearly stated as future work of interest in the conclusion : 'It has to be noticed that the method would gain to be tested on larger dataset with, for instance, motorcycles, and other noisy traffic elements which are not considered in this study.'

@@

\item \emph{Is also interesting to know if the distribution of microphones in a realistic noise level measurement scenario is taken into account during the simulations.}

$\rightarrow$ The purpose of this study is to propose a tool that could be integrated into a sensor network. The distribution of the microphone is not a question dealt with in this work. The proposed method is designed to perform with a monophonic input. That being said, considering the inputs of multiple sensors may help to achieve more consistent estimates. This is left for potential future work.

@@

\item \emph{"The obtained dictionary is expressed with third octave bands", "The spectrogram V, as the dictionary W, is expressed with third octave bands (F = 29)." - please, clarify. Perhaps is better to join the description of this representation with the section 4.2.1.}

$\rightarrow$ The manuscript have been updated, see Section 4.2.2: 'The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed with third octave bands ($F$ = 29). This coarser method allows us to reduce the dimensionality and then decrease the computation time. Furthermore, by expressing the frequency axis on a log frequency axis, the low frequencies, where the traffic energy is focused, are described more finely than the high frequencies. Experimental validation consistently showed that considering third octave bands do not impact the performance of the estimator studied in this paper. But, most of all, it is a suited representation to this sound environment as this kind of representation is widely used in the urban acoustic field, compared to MFCCs for instance.'

@@

\item \emph{As for the sound level calculation itself, it is not clear if A-weighting is applied.}

$\rightarrow$ As now explicitly stated in Section 4.2.2, 'The $A$-weighting of the sound levels is not considered here as it decreases the low frequencies levels where the road traffic components are mainly present.'

@@

\item \emph{Also, the terminology is a bit confusing. E.g. Figure 8 "1 second equivalent sound pressure level" - to my understanding, the equivalent sound pressure level Leq is an average over the specified period of time and, therefore, would correspond to a single value. If the goal is to eventually simulate the output of a sound pressure level meter, some calibration would be needed.}

$\rightarrow$ The caption of the Figure 8 has been corrected ('Evolution of 1 second equivalent sound pressure levels'). The calibration step is here not necessary as all the sound level are relatives.

@@

\item \emph{It is not clear what is the number of iterations that was used for each NMF version. It might make sense to use the reduced number of iterations for Sup-NMF as it is done for TI-NMF.}

$\rightarrow$ As stated in Section 4.2.2, 100 iterations are performed for every NMF types.

@@

\item \emph{Is it true that the dictionaries W in Sup-NMF, Ws in Sem-NMF and W0 in TI-NMF are the same? Authors may want to state it clearly in Section 4.2.1.}

$\rightarrow$ Yes it is, it has been clarified in the updated version of the manuscript in Section 4.2.1: 'The 10 versions of the built dictionary are then used for NMF. In Sup-NMF, these 10 versions correspond to $\mathbf{W}$, in Sem-NMF, they correspond to the fixed part $\mathbf{W_s}$ and for TI-NMF, they are the initial dictionaries $\mathbf{W_0}$ that are next updated.'

@@

\item \emph{Figure 5 caption, "experience" should be "experiment"?}

$\rightarrow$ Indeed, fixed.

\item \emph{"The choice of the dimensions is often made so that F × K + K × N $<$ F × N ." - could you please provide a reference for this statement? }

$\rightarrow$ The reference \cite{fevotte_nonnegative_2009} is added.

@@

\item \emph{"must of all" should probably be "most of all" }

$\rightarrow$ Indeed, fixed.

\item \emph{"The errors are too important for low TIR and this for all the sub-classes." - the sentence is not clear.}

$\rightarrow$ The sentence is rewritten to: 'Errors are too important for all sub-classes at low $TIR$.'

\bibliographystyle{spmpsci}      % mathematics and physical sciences
%\bibliographystyle{spphys}       % APS-like style for physics
\bibliography{bibliographie_jasm}

\end{document}

### 2018-08-31 revision/gloaguenNmfTraffic_v2.tex
done with proof rerad of response

100 iterations are performed for all NMF. The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed with third octave bands ($F$ = 29). This coarser method allows us to reduce the dimensionality and then decrease the computation time. Furthermore, by expressing the frequency axis on a log frequency axis, the low frequencies, where the traffic energy is focused, are described more finely than the high frequencies. Experimental validation consistently showed that considering third octave bands do not impact the performance of the estimator studied in this paper. But, most of all, it is a suited representation to this sound environment as this kind of representation is widely used in the urban acoustic field, compare to MFCC for instance. For TI-NMF, a preliminary study showed that the threshold $t$ value range can be evaluated between  0.30 and 0.70. An increment step of 0.01 has been considered as being sufficiently precise. Table \ref{tab:experimental_factorsNMF} summarize the experimental factors and their related modalities.

@@

In this work the non negative matrix factorization framework is used to estimate the road traffic sound level in urban sound mixtures. It is a well suited approach to these sound environments because it easily takes into account the overlap between the multiple sound sources present in the cities and it is adapted to monophonic sensor networks. Different versions of NMF have been studied as a supervised and semi-supervised approach. On a large corpus of sounds, the supervised approach proves to be too restrictive to be adapted to different sound environments whereas the semi-supervised approach has, on the contrary, too many degrees of freedom on the mobile dictionary $\mathbf{W_r}$, decreasing its performance especially when the traffic is predominant. The proposed approach, named threshold initialized NMF achieves the lowest average error on the entire corpus. With this method, the $\mathbf{W}$ is initialized with road traffic spectra, updated and the dictionary elements that are similar to the road traffic spectra are then extracted by hard thresholding.
The study of the error according each $TIR$ reveals that this method is not the most efficient on each $TIR$, but it has to be remind that, this parameter is not available in practical case. TI-NMF can be considered as the approach that limit the error in the different environment.
A major advantage of the proposed approach is that it is not designed for a specific source. It has to be noticed that the method would gain to be tested on larger dataset with, for instance, motorcycles, noisy traffic elements which are absent here. However, even though the experiments described in this paper focused on road traffic sounds, changing the dictionary to contain bird sounds would lead to an estimator of the presence of birds. Extending the apporach to other sources is thus of interest for future research. Also, performance improvement could be achieved by the addition of constraints such as sparsness \cite{hoyer2004non} and smoothness \cite{virtanen_monaural_2007} of the low rank matrices.

>>>>

100 iterations are performed for every NMF types. The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed with third octave bands ($F$ = 29). This coarser method allows us to reduce the dimensionality and then decrease the computation time. Furthermore, by expressing the frequency axis on a log frequency axis, the low frequencies, where the traffic energy is focused, are described more finely than the high frequencies. Experimental validation consistently showed that considering third octave bands do not impact the performance of the estimator studied in this paper. But, most of all, it is a suited representation to this sound environment as this kind of representation is widely used in the urban acoustic field, compared to MFCCs for instance. For TI-NMF, a preliminary study showed that the threshold $t$ value range can be evaluated between  0.30 and 0.70. An increment step of 0.01 has been considered as being sufficiently precise. Table \ref{tab:experimental_factorsNMF} summarize the experimental factors and their related modalities.

@@

In this work the non negative matrix factorization framework is used to estimate the road traffic sound level in urban sound mixtures. It is a well suited approach to these sound environments because it easily takes into account the overlap between the multiple sound sources present in the cities and it is adapted to monophonic sensor networks. Different versions of NMF have been studied as a supervised and semi-supervised approach. On a large corpus of sounds, the supervised approach proves to be too restrictive to be adapted to different sound environments whereas the semi-supervised approach has, on the contrary, too many degrees of freedom on the mobile dictionary $\mathbf{W_r}$, decreasing its performance especially when the traffic is predominant. The proposed approach, named threshold initialized NMF achieves the lowest average error on the entire corpus. With this method, the $\mathbf{W}$ is initialized with road traffic spectra, updated and the dictionary elements that are similar to the road traffic spectra are then extracted by hard thresholding.
The study of the error according each $TIR$ reveals that this method is not the most efficient on each $TIR$, but it has to be remind that, this parameter is not available in practical case. TI-NMF can be considered as the approach that limit the error in the different environment.
A major advantage of the proposed approach is that it is not designed for a specific source. It has to be noticed that the method would gain to be tested on larger dataset with, for instance, motorcycles, and other noisy traffic elements which are not considered in this study. However, even though the experiments described in this paper focused on road traffic sounds, changing the dictionary to contain bird sounds would lead to an estimator of the presence of birds. Extending the apporach to other sources is thus of interest for future research. Also, performance improvement could be achieved by the addition of constraints such as sparsness \cite{hoyer2004non} and smoothness \cite{virtanen_monaural_2007} of the low rank matrices.
